---
title: "WGCNA of Pc timecourse"
author: "BSchroeter"
date: "2023-03-20"
output:
  html_document:
    toc: yes
    df_print: paged
  prettydoc::html_pretty:
    theme: hpstr
    highlight: github
  html_notebook:
    theme: lumen
    toc: yes
    toc_float: yes
---

# Purpose

1. Build a weighted and directed network of genes based on the Dual RNA seq data generated from the timecourse of Phytophthora cinnamomi and Lupinus angustifolius 
2. Determine modules (clusters of genes) from the network associated to disease progression (for example, biotrophic or necrotrophic stages) 
3. Extract the names of the genes from these hubs and compare them to the genes in the literature 
4. Functionally annotate these genes

Working idea: This network will then be used to identify hub genes for each of the early, middle and late interactions.

## Load Libraries

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=TRUE}
suppressPackageStartupMessages({c(
library(WGCNA),
library(DESeq2),
library(GEOquery),
library(tidyverse),
library(gridExtra),
library(reshape2),
library(rtracklayer),
library(dplyr))})
```

Load Phytophthora cinnamomi gtf file, clean up to get Gene IDs

Combine alternatively spliced transcripts (seen in transcript_id as -RA and RB)

```{r}
pc.gtf <- rtracklayer::import("https://ftp.ncbi.nlm.nih.gov/genomes/genbank/protozoa/Phytophthora_cinnamomi/latest_assembly_versions/GCA_018691715.1_ASM1869171v1/GCA_018691715.1_ASM1869171v1_genomic.gtf.gz")
pc.df <- as.data.frame((pc.gtf))

pc.genes <- filter(pc.df, type == "start_codon")
pc.geneids <- select(pc.genes, gene_id, product, protein_id)  

pc.annotations <- pc.geneids %>% 
  distinct(gene_id, .keep_all = T)
nrow(pc.annotations)

pcannot <- as.matrix(pc.annotations)

#write.table(pcannot, file = "pcgeneids.tsv",quote=FALSE,sep="\t")
```

Load GO terms blasted from Omicsbox 
```{r}
goterms <- read.delim('pc.goterms.txt', header = TRUE) %>%
  select(c(SeqName, GO.IDs, GO.Names, Description))
  
head(goterms)

colnames(goterms) <- c("protein_id", "GO_terms", "GO_descripton", "description")

goterms.df <- dplyr::right_join(goterms, pc.annotations, by = 'protein_id')
nrow(goterms.df)
```

Make GO term list for enrichment analysis

```{r}
splitgt.df <- as.tibble(goterms.df) %>%
  separate_longer_delim(c(GO_terms, GO_descripton), delim = ";")

splitgt.df <- as.data.frame(splitgt.df)

#strip leading spaces
splitgt.df$GO_terms <- gsub(" ","",splitgt.df$GO_terms)
splitgt.df$GO_descripton <- gsub("^ ","",splitgt.df$GO_descripton)
head(splitgt.df, 10)

gu <- unique(splitgt.df$GO_terms)
head(gu,20)

gul <- lapply(1:length(gu), function(i){
  mygo <- gu[i]
  unique(splitgt.df[splitgt.df$GO_terms == mygo, "gene_id"])
})

names(gul) <- lapply(1:length(gu), function(i){
  mygo <- gu[i]
  desc <- head(splitgt.df[splitgt.df$GO_terms == mygo, "GO_descripton"],1)
  id_desc <- paste(mygo,desc)
})

head(names(gul))

```

Assemble count matrix and coldata file

```{r, echo=FALSE}
tmp<-read.table("3col.tsv.gz",header=F)
x<-as.matrix(acast(tmp, V2~V1, value.var="V3"))
colnames(x)<-sapply(strsplit(colnames(x),"_"),"[[",1)

#head(x)
#write.table(x,file="countmatrix.tsv",quote=FALSE,sep="\t")
```

Import files into r

```{r}
coldata <- read.table('sample_info.tsv')
Pcgenenames <- read.table('pcgeneids.tsv', row.names = 1, quote = "", sep='\t', fill = TRUE, header = TRUE)
IUM83Tanjilcountmatrix <- read.table('countmatrix.tsv') 
```

Clean countmatrix for P. cinnamomi analysis

```{r}
collabels <- colnames(IUM83Tanjilcountmatrix) <- (coldata$Sample)
colnames(IUM83Tanjilcountmatrix) <- collabels

IUM83Tanjilcountmatrix <- tibble::rownames_to_column(IUM83Tanjilcountmatrix, "gene_id")

IUM83CountMatrix <- IUM83Tanjilcountmatrix %>% 
  filter(str_detect(gene_id, "IUM83")) 
  
rownames(IUM83CountMatrix) <- IUM83CountMatrix$gene_id
IUM83CountMatrix <- IUM83CountMatrix [ ,-1]
IUM83CountMatrix <- as.data.frame(IUM83CountMatrix)
IUM83CountMatrix <- IUM83CountMatrix[ ,-(1:12)]

#write.table(IUM83CountMatrix, file = "Pc_countmatrix.tsv",quote=FALSE,sep="\t")
```

Clean coldata for Deseq2 normalisation

```{r}
colData <- coldata %>% 
  filter(str_detect(Sample, "Pc"))

rownames(colData) <- colData$Sample
colData <- colData [ ,-1] 
```

Detect and remove outlier genes

```{r}
#Call a function from WGCNA package that detects outliers 
#Rows should be the samples and the columns genes
gsg <- goodSamplesGenes(t(IUM83CountMatrix))
summary(gsg)

#If false, then there are outliers
gsg$allOK #False

table(gsg$goodGenes) #3012to be excluded
table(gsg$goodSamples) #All 12 samples passed

# remove genes that are detectd as outliers
data <- IUM83CountMatrix[gsg$goodGenes == TRUE,]
```

Detect outlier samples

```{r}
# detect outlier samples - hierarchical clustering
htree <- hclust(dist(t(data)), method = "average")
groups <- cutree(htree, k=2) # cut tree into clusters

plot(htree, labels(groups))
# draw dendogram with red borders around the clusters
rect.hclust(htree, k=2, border="red")
```

PCA showing clusters

```{r}
pca <- prcomp(t(data))
pca.dat <- pca$x

pca.var <- pca$sdev^2
pca.var.percentage <- round(pca.var/sum(pca.var)*100, digits = 2)

pca.dat <- as.data.frame(pca.dat)

ggplot(pca.dat,aes(PC1, PC2)) +
  geom_point() +
  geom_text(label = row.names(pca.dat)) + 
  labs(x = paste0('PC1: ', pca.var.percentage[1], ' %'),
       y = paste0('PC2: ', pca.var.percentage[2], ' %'))
```

Remove outlier samples

```{r}
clusters <- as.data.frame(groups)
head(clusters)
table(clusters)

# the biggest cluster is cluster 2 and the rest will be tagged as outliers
outliers <- clusters %>% filter(., !groups == 2) %>% row.names()

# exclude outlier samples
data.subset <- data[,!(colnames(data) %in% outliers)]
```

# Normalisation using DESeq2 package

The WGCNA library requires normalisation using the vst (variance-stabilising transform) function from the DESeq2 package

```{r}
# exclude outlier samples from the column data to match the new data
colData <- colData %>% 
  filter(!row.names(.) %in% outliers)

# making sure the rownames and column names identical for the two data sets
all(rownames(colData) == colnames(data.subset))

# create DESeq Data Set
dds <- DESeqDataSetFromMatrix(countData = data.subset,
                              colData = colData,
                              design = ~ 1) # no model, for normalisation only

# remove all genes with counts < 10 in more than 90% of samples (12*0.9=10.8 ~ 11) as suggested by WGCNA on RNAseq FAQ (https://horvath.genetics.ucla.edu/html/CoexpressionNetwork/Rpackages/WGCNA/faq.html)
# <10 in more than 90% samples
dds90 <- dds[rowSums(counts(dds) >= 10) >= 8,]
nrow(dds90) # 5403 genes

# >= 15) >= 9,] 8084 genes
# >= 10) >= 9,] 8911 genes 
# >= 10) >= 11,] 5403 genes <===== #less than 10 counts in %90 of samples
# >= 15) >= 11,] 4420 genes 

gene.list <- row.names(dds90)
#lapply(gene.list, write, "all_genes.txt", append=TRUE)

# perform variance stabilization
dds_norm <- vst(dds90)

# get normalized counts
norm.counts <- assay(dds_norm) %>% 
  t()

#Save normalised dataset for faster analysis next time
saveRDS(norm.counts, "norm.counts.rds")
```

# Network Construction

```{r}
# load norm.counts object
#norm.counts <- readRDS("norm.counts")

# Choose a set of soft-thresholding powers to create a scale-free network
power <- c(c(1:10), seq(from = 12, to = 30, by = 2))

# Call the network topology analysis function
sft <- pickSoftThreshold(norm.counts,
                  powerVector = power,
                  networkType = "signed",
                  RsquaredCut = 0.8,
                  verbose = 5)

sft.data <- sft$fitIndices

a1 <- ggplot(sft.data, aes(Power, SFT.R.sq, label = Power)) +
  geom_point() +
  geom_text(nudge_y = 0.1) +
  geom_hline(yintercept = 0.80, color = 'red') +
  labs(x = 'Power',
       y = 'Scale free topology model fit, signed R^2',
       title = 'Scale independence') +
  theme_classic()

a2 <- ggplot(sft.data, aes(Power, mean.k., label = Power)) +
  geom_point() +
  geom_text(nudge_y = 0.1) +
  labs(x = 'Power',
       y = 'Mean Connectivity',
       title = 'Mean connectivity') +
  theme_classic()
  
grid.arrange(a1, a2, nrow = 2) 

soft_power <- sft$powerEstimate ### 16

#soft_power <- 16
```

Create network and identify modules

Note: this chunk is set not to run since the blockwise Modules function takes a long time to run. The R object has been saved and is loaded in the next chunk for a faster run time.

```{r eval=FALSE, include=FALSE}
# convert matrix to numeric
norm.counts[] <- sapply(norm.counts, as.numeric)

#Successively, hierarchical clustering was performed to identify modules
temp_cor <- cor
cor <- WGCNA::cor

# Parameters to be tweaked later
bwnet <- blockwiseModules(norm.counts,
                 maxBlockSize = 7500, # selected total number of genes since CPU memory is sufficient (32GB workstation should be able to handle perhaps 30000)
                 TOMType = "signed",
                 power = soft_power,
                 mergeCutHeight = 0.20,
                 saveTOMs = TRUE,
                 saveTOMFileBase = "pc_TOM",
                 numericLabels = FALSE, # set as false to assign color as labels
                 randomSeed = 1243, # for reproducibility since this function uses clustering
                 verbose = 3)

# Save bwnet object
saveRDS(bwnet, "bwnet.rds")

cor <- temp_cor
```

```{r}
# load bwnet object
bwnet <- readRDS("bwnet.rds")

module_eigengenes <- bwnet$MEs %>%
  orderMEs(.)

head(module_eigengenes)


# Plot the dendrogram and the module colors before and after merging underneath
plotDendroAndColors(bwnet$dendrograms[[1]], cbind(bwnet$unmergedColors, bwnet$colors),
                    c("unmerged", "merged"),
                    dendroLabels = FALSE,
                    addGuide = TRUE,
                    hang= 0.03,
                    guideHang = 0.05)

 # grey module = all genes that doesn't fall into other modules
 
module.total <- table(bwnet$colors)
```

# Relate the modules to stages

```{r}
# create traits file - assign 1 if a sample is a certain stage, else assign 0
#Dis_traits <- colData %>% 
#  mutate(Dis.vs.all = ifelse(grepl('Treated', Treatment), 1, 0)) %>% 
#  select(4)


factor_levels <- unique(colData$Stage)

# transform stages into factors and define levels
colData$Stage <- factor(colData$Stage, levels = factor_levels)

traits <- binarizeCategoricalColumns(colData$Stage,
                           dropFirstLevelVsAll = FALSE,
                           includePairwise = FALSE,
                           includeLevelVsAll = TRUE,
                           minCount = 1)

rownames(traits) <- colData$Sample
```

# Visualise module-trait association as a heatmap

```{r r, fig.width=8, fig.height=12}
# Define numbers of genes and samples
nSamples <- nrow(norm.counts)
nGenes <- ncol(norm.counts)

# correlation for module eigengenes and traits
module.trait.corr <- cor(module_eigengenes, traits, use = 'p')
module.trait.corr.pvals <- corPvalueStudent(module.trait.corr, nSamples)

# Heat map v2 (from WGCNA tutorial)
textMatrix =  paste(signif(module.trait.corr, 2), "\n(",
                    signif(module.trait.corr.pvals, 1), ")", sep = "")
dim(textMatrix) = dim(module.trait.corr)



par(mar = c(6, 8.5, 3, 3));
labeledHeatmap(Matrix = module.trait.corr,
               xLabels = colnames(module.trait.corr),
               yLabels = rownames(module.trait.corr),
               ySymbols = rownames(module.trait.corr),
               colorLabels = FALSE,
               colors = blueWhiteRed(50),
               textMatrix = textMatrix,
               textAdj = c(0.5, 0.5),
               setStdMargins = FALSE,
               cex.lab.y = 0.6,
               cex.text = 0.7,
               zlim = c(-1,1),
               main = paste("Module-trait relationships"))



# get number of genes for each module
table(bwnet$colors)

#Tag genes with module membership and store it in a table
module.gene.mapping <- as.data.frame(bwnet$colors)
module.gene.mapping

Early <- module.gene.mapping %>% 
  filter(`bwnet$colors` == 'pink') %>% 
  rownames()
```

Significance in brackets shows how significantly associated the module (cluster of genes) is the trait of interest  
Find modules that have significant association with disease state

Calculate the module membership and the associated p-values
The module membership/intramodular connectivity is calculated as the correlation of the eigengene and the gene expression profile.
This quantifies the similarity of all genes on the array to every module.

Using the gene significance you can identify genes that have a high significance for trait of interest 
Using the module membership measures you can identify genes with high module membership in interesting modules.

# Gene Significance at the Early Pc-lupin interaction

```{r}
# Define a gene significance variable for Early
GS.Early <- as.numeric(cor(norm.counts, traits$data.Early.vs.all, use = "p"))

# This translates the numeric values into colors
GS.stage_earlyColor = numbers2colors(GS.Early, signed = T)
blocknumber = 1

moduleLabelsAutomatic = bwnet$colors
# Convert labels to colors for plotting
moduleColorsAutomatic = labels2colors(moduleLabelsAutomatic)

datColors = data.frame(bwnet$colors, GS.stage_earlyColor)[bwnet$blockGenes[[blocknumber]], 
    ]

# Plot the dendrogram and the module colors underneath
plotDendroAndColors(bwnet$dendrograms[[blocknumber]], colors = datColors, groupLabels = c("Module colors", 
    "GS.stage.Early"), dendroLabels = FALSE, hang = 0.03, addGuide = TRUE, guideHang = 0.05)
```

```{r}
datKME <- signedKME(norm.counts, module_eigengenes)

# Measure the correlation of the gene's module membership and the associated p-values
module.membership.measure <- cor(module_eigengenes, norm.counts, use = 'p')
module.membership.measure.pvals <- corPvalueStudent(module.membership.measure, nSamples)

# Calculate the gene significance and associated p-values
early.gene.signf.corr <- cor(norm.counts, traits$data.Early.vs.all, use = 'p')
early.gene.signf.corr.pvals <- corPvalueStudent(early.gene.signf.corr, nSamples)


colorOfColumn = substring(names(datKME), 4)
selectModules = c("brown", "magenta", "blue", "turquoise", "lightcyan")
#selectModules = colorOfColumn[colorOfColumn !="grey"]

#par(mfrow = c(4, length(selectModules)/4))
  for (module in selectModules) {
      column = match(module, colorOfColumn)
      restModule = moduleColorsAutomatic == module
      verboseScatterplot(datKME[restModule, column], GS.Early[restModule], xlab = paste("Module Membership", 
          module, "module"), ylab = "GS.stage_Early", main = paste("kME.", module, 
          "vs. GS"), col = module)
  }
```
choose top 5 modules (not grey) based on the model significance to the trait 
```{r}
GSEarly <- early.gene.signf.corr %>% 
  as.data.frame() %>%
  tibble::rownames_to_column("gene_id") %>% 
  arrange(V1) %>% 
  head(50)

EarlyDIS <- dplyr::right_join(Pcgenenames, GSEarly, by = 'gene_id')
EarlyDIS %>%
  arrange(V1) %>%
  head(50)


colorgene.id <- datColors %>% 
  tibble::rownames_to_column("gene_id")
  

EarlyDIS.color <- dplyr::right_join(colorgene.id, GSEarly, by = 'gene_id')

```


# Gene Significance at the Mid Pc-lupin interaction

```{r}
# Define a gene significance variable for Early
GS.mid <- as.numeric(cor(norm.counts, traits$data.Middle.vs.all, use = "p"))

# This translates the numeric values into colors
GS.stage_midColor = numbers2colors(GS.mid, signed = T)
blocknumber = 1

moduleLabelsAutomatic = bwnet$colors
# Convert labels to colors for plotting
moduleColorsAutomatic = labels2colors(moduleLabelsAutomatic)

datColors = data.frame(bwnet$colors, GS.stage_midColor)[bwnet$blockGenes[[blocknumber]], 
    ]

# Plot the dendrogram and the module colors underneath
plotDendroAndColors(bwnet$dendrograms[[blocknumber]], colors = datColors, groupLabels = c("Module colors", 
    "GS.mid"), dendroLabels = FALSE, hang = 0.03, addGuide = TRUE, guideHang = 0.05)
```
```{r}
datKME <- signedKME(norm.counts, module_eigengenes)

# Measure the correlation of the gene's module membership and the associated p-values
module.membership.measure <- cor(module_eigengenes, norm.counts, use = 'p')
module.membership.measure.pvals <- corPvalueStudent(module.membership.measure, nSamples)

# Calculate the gene significance and associated p-values
mid.gene.signf.corr <- cor(norm.counts, traits$data.Middle.vs.all, use = 'p')
mid.gene.signf.corr.pvals <- corPvalueStudent(mid.gene.signf.corr, nSamples)


colorOfColumn = substring(names(datKME), 4)
selectModules = c("red", "tan", "salmon","green", "magenta")
#selectModules = colorOfColumn[colorOfColumn !="grey"]

#par(mfrow = c(3, length(selectModules)/3))
  for (module in selectModules) {
      column = match(module, colorOfColumn)
      restModule = moduleColorsAutomatic == module
      verboseScatterplot(datKME[restModule, column], GS.mid[restModule], xlab = paste("Module Membership", 
          module, "module"), ylab = "GS.stage_mid", main = paste("kME.", module, 
          "vs. GS"), col = module)
  }
```

```{r}
GSMid <- mid.gene.signf.corr %>% 
  as.data.frame() %>%
  tibble::rownames_to_column("gene_id") %>% 
  arrange(V1) %>% 
  head(50)

MidDIS <- dplyr::right_join(Pcgenenames, GSMid, by = 'gene_id')
MidDIS %>%
  arrange(V1) %>%
  head(50)


MidDIS.color <- dplyr::right_join(colorgene.id, GSMid, by = 'gene_id')


```

# Gene Significance at the Late Pc-lupin interaction

```{r}
# Define a gene significance variable for Early
GS.late <- as.numeric(cor(norm.counts, traits$data.Late.vs.all, use = "p"))

# This translates the numeric values into colors
GS.stage_lateColor = numbers2colors(GS.late, signed = T)
blocknumber = 1

moduleLabelsAutomatic = bwnet$colors
# Convert labels to colors for plotting
moduleColorsAutomatic = labels2colors(moduleLabelsAutomatic)

datColors = data.frame(bwnet$colors, GS.stage_lateColor)[bwnet$blockGenes[[blocknumber]], 
    ]

# Plot the dendrogram and the module colors underneath
plotDendroAndColors(bwnet$dendrograms[[blocknumber]], colors = datColors, groupLabels = c("Module colors", 
    "GS.stage.Late"), dendroLabels = FALSE, hang = 0.03, addGuide = TRUE, guideHang = 0.05)
```

```{r}
datKME <- signedKME(norm.counts, module_eigengenes)

# Measure the correlation of the gene's module membership and the associated p-values
module.membership.measure <- cor(module_eigengenes, norm.counts, use = 'p')
module.membership.measure.pvals <- corPvalueStudent(module.membership.measure, nSamples)

# Calculate the gene significance and associated p-values
late.gene.signf.corr <- cor(norm.counts, traits$data.Late.vs.all, use = 'p')
late.gene.signf.corr.pvals <- corPvalueStudent(late.gene.signf.corr, nSamples)


colorOfColumn = substring(names(datKME), 4)

selectModules = c("green", "turquoise", "blue", "grey60", "salmon")
#selectModules = colorOfColumn[colorOfColumn !="grey"]

#par(mfrow = c(3, length(selectModules)/3))
  for (module in selectModules) {
      column = match(module, colorOfColumn)
      restModule = moduleColorsAutomatic == module
      verboseScatterplot(datKME[restModule, column], GS.late[restModule], xlab = paste("Module Membership", 
          module, "module"), ylab = "GS.stage_Late", main = paste("kME.", module, 
          "vs. GS"), col = module)
  }
```

```{r}
GSLate <- late.gene.signf.corr.pvals %>% 
  as.data.frame() %>%
  tibble::rownames_to_column("gene_id") %>% 
  arrange(V1) %>% 
  head(50)

LateDIS <- dplyr::right_join(Pcgenenames, GSLate, by = 'gene_id')
LateDIS %>%
  arrange(V1) %>%
  head(50)

LateDIS.color <- dplyr::right_join(colorgene.id, GSLate, by = 'gene_id')

```

```{r}

# chooseTopHubInEachModule returns the gene in each module with the highest connectivity, looking at all genes in the expression file

PcHubgenes <- chooseTopHubInEachModule(norm.counts,
                         colorh = module.gene.mapping,
                         omitColor = "grey",
                         power =  2,
                         type = "signed")
PcHubgenes 

PcHubgenes.df <- PcHubgenes %>% 
  as.data.frame(row.names = NULL, stringAsFactors = FALSE) 

PcHubgenes.df <- PcHubgenes.df %>% 
       rename("gene_id" = ".")

PcHubgenes.df <- tibble::rownames_to_column(PcHubgenes.df, "module")


PcHubgenes.df <- dplyr::right_join(pc.annotations, PcHubgenes.df, by = 'gene_id')
PcHubgenes.df
```

# Export to Cytoscape

```{r}
load("pc_TOM-block.1.RData")


TOM.mat = as.matrix(TOM)
# choose module
module = "cyan"
# get list of genes
probes = names(as.data.frame(norm.counts))

moduleColors = labels2colors(bwnet$colors)

inModule <- (moduleColors==module)
modProbes = probes[inModule]
# Select the corresponding Topological Overlap
modTOM = TOM.mat[inModule, inModule]

# Export the network into edge and node list files for Cytoscape
cyt = exportNetworkToCytoscape(modTOM,
  edgeFile=paste("CytoEdge",paste(module,collapse="-"),".txt",sep=""),
  nodeFile=paste("CytoNode",paste(module,collapse="-"),".txt",sep=""),
  weighted = TRUE, threshold = 0.02,nodeNames=modProbes,
  nodeAttr = moduleColors[inModule])
```

#``{r}
edge.annotation <- as.data.frame(apply(pc.annotations,              # Remove spaces within protein ID 
                                 2,
                                 function(x) gsub("\\s+", "", x)))
edge.annotation                                           

edge <- read.delim("CytoEdgelightgreen.txt")
colnames(edge)
colnames(edge) <- c("source", "target","weight","direction","fromAltName","toAltName")

node <- read.delim("CytoNodelightgreen.txt")
colnames(node)  
colnames(node) <- c("gene_id","altName","node_attributes") 
nodeID <- dplyr::right_join(edge.annotation, node, by = 'gene_id')
nodeID

write.csv(nodeID, file = 'lightgreennode.txt')
#```






#```{r}
datExpr <- norm.counts
# Calculate eigengenes
MEList = moduleEigengenes(datExpr, colors = bwnet$colors)
MEs = MEList$eigengenes
# Calculate dissimilarity of module eigengenes
MEDiss = 1-cor(MEs);
# Cluster module eigengenes
METree = hclust(as.dist(MEDiss), method = "average");
# Plot the result
sizeGrWindow(7, 6)
plot(METree, main = "Clustering of module eigengenes",
     xlab = "", sub = "")

#```
#```{r}
# Heatmap of old module eigen-genes and samples
#pdf(file="oldMEs.pdf",heigh=80,width=20)
library("pheatmap")
rownames(MEs)=names(IUM83CountMatrix[,9])
pheatmap(MEs,cluster_col=T,cluster_row=T,show_rownames=F,show_colnames=T,fontsize=6)



# Heatmap of new module eigen-genes and sample trait (e.g. Zone)
col_ann <- colData[,c(1,3)]
rownames(col_ann) <- col_ann[,1]
col_ann <- data.frame(col_ann)
col_ann$Stage <- as.factor(col_ann$Stage)
col_ann <- col_ann[order(col_ann$Stage),]
col_ann$sample_ID <- NULL
head(col_ann)
ann_color <- list("col_ann" = c("Control" = "yellow",
                                "Early" = "red",
                                "Middle" = "green",
                                "Late" = "blue"))

data <- data.frame(MEs)
data <- data[order(match(rownames(data), rownames(col_ann))),]
dim(MEs)

#pdf(file="newMEs.pdf",heigh=60,width=20)
rownames(MEs)=names(colData[ ,1])
pheatmap(data,cluster_col=T,cluster_row=F,show_rownames=F,
         show_colnames=T,fontsize=6,
         annotation_row = col_ann, annotation_colors = ann_color)
#```




### Session Information

```{r Session Info, echo=FALSE}
sessionInfo()
```
